### 2021-06-11 README.Rmd
updates to README.Rmd

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Assessment of Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon"
Authors <- "See, Kevin E., Nick Porter, Richard A. Carmichael, and Michael W. Ackerman"
yr <- 2021
Journal <- "TBD"
```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BiomarkABS/DeadwaterPaper/master?urlpath=rstudio)

@@

## How to run in your broswer or download and run locally

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon Populations"
Authors <- "Carmichael, Richard A., Kevin E. See, Nick Porter, and Michael W. Ackerman"
yr <- 2021
Journal <- "TBD"

```

@@

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BiomarkABS/DeadwaterPaper/main?urlpath=rstudio)

@@

## How to run in your browser or download and run locally
